---
title: "wordle.Rmd"
author: "Sydney Jansen and Jennie DeVore"
date: "2024-02-12"
output: html_document
---

# Exercise 04: Program a Word Game

Run the code chunk below (**Step_1**) to load two lists of words, **solution_list** and **valid_list**.

```{r include=FALSE}

library(tidyverse)
library(dplyr)

# use links to a public repo because it liked the links to end in .txt instead of the token when the repo was set to private
file1 <- "https://raw.githubusercontent.com/jennieandbird/exercise-04/main/collins-scrabble-words-2019.txt"
file2 <- "https://raw.githubusercontent.com/jennieandbird/exercise-04/main/google-10000-english-usa-no-swears.txt"

# Create your own custom function called load_dictionary() that takes a single argument, “filename”, that can be used to read in either of the two data files you downloaded.

#Step 1: Create Function
load_dictionary <- function(filename) {
  v1 <- readLines(filename)}

# Once you have created your function, use that function to create two variables, solution_list and valid_list, that, respectively contain vectors of possible solution words and valid words to guess. That is, you should be able to run the following to create these two vectors

valid_list <- load_dictionary(file1)
solution_list <- load_dictionary(file2)

# Running str(valid_list) should return… chr [1:279496] "AA" "AAH" "AAHED" "AAHING"...
# Running str(solution_list) should return… chr [1:8336] "THE" "OF" "AND" "TO"...

str(valid_list)
# running this does say... chr [1:279496] "AA" "AAH" "AAHED" "AAHING" ..." ...so that's good!
str(solution_list)
# and this one says... chr [1:9884] "THE" "OF" "AND" "TO" ... ... also good!

# Step 1 complete! (I think!)

```

Next, run the code chunk below (**Step_2**) to make sure the **solution_list** only includes words that also appear on **valid_list**.

```{r include=FALSE}
# Winnow your variable solution_list to only include words that are included in valid_list. There are multiple ways that you could do this, but the set operation function, intersection() is an easy way. Use R help to look at the documentation for the intersection() function to see if you can get that to work. 

solution_list <- intersect(valid_list, solution_list)

# How many words are in your updated solution_list vector?

print(solution_list)

# solution_list updated to include 8336 words, down from 9884 words.

```

Running this code chunk (**Step_3**) will create a function (**pick_solution**) that randomly picks a word for you to guess. It will save that word as a list of letters (**solution**) and a vector of letters (**solutionvector**).

```{r include=FALSE}
# Write a custom function called pick_solution() that [1] removes all words from solution_list that are not 5 letters in length, [2] then randomly chooses a single word from those that remain, and [3] then splits that word into a vector of single-character elements. You should be able to pass your solution_list vector as the argument to the function.

pick_solution <- function(solution_list){
  # [1] remove all words that are not 5 letters in length
  five_letter_words <- solution_list[nchar(solution_list) == 5]
  # [2] randomly choose a single word
  chooseword <- sample(five_letter_words, 1)
  # [3] split that word into a vector
  str_extract_all(chooseword, boundary("character"))
}

# Once your function works, run it and assign the result to a variable called solution.
# solution <- pick_solution(solution_list)

solution <- pick_solution(solution_list)
# realized this was a list when it should be a vector!
solutionvector <- unlist(solution)

```

Now it's time to guess the word! Run the code chunk below (**Step_4**) to begin.

```{r include=FALSE}
# Now, to tackle the bulk of the problem, create two more functions. The first should be called play_wordle() and it should take three arguments: [1] the answer to the puzzle (the value of your solution variable), [2] a list of valid guesses (the contents of your valid_list variable), and [3] a value for “number of guesses”, which you should set to the original Wordle game default of 6.

evaluate_guess <- function(guess_vector, solutionvector){
# set up a placeholder vector with 5 spaces
  hintvector <- c(1, 2, 3, 4, 5)
# identify the spots that are correct letter and correct order; mark them with "*"
  for (i in 1:5) {
   if (guess_vector[i] == solutionvector[i]) {
     hintvector[i] <- "*"}}
# identify the letters that exist in the word (in any order); mark them with "+"
# also, mark the leftover letters with "-" to indicate they're not in the solution
  for (i in 1:5) {
    if (hintvector[i] != "*") {
      lettersinword <- match(guess_vector[i], solutionvector)
      if (!is.na(lettersinword)) {
        hintvector[i] <- "+"}
      else {hintvector[i] <- "-"}}}
 return(hintvector)}

play_wordle <- function(solutionvector, valid_list, num_guesses = 6){
  print("You have 6 chances to guess a 5-letter word.")
  letters_remaining <- LETTERS
  guesses <- 0
    while(guesses < num_guesses) {
      guess <- toupper(readline(prompt = "Try to guess the word: "))
# Validate the guess
      if(nchar(guess) != 5) {
      print("Word needs to be 5 letters long.")
      } else if(!(guess %in% valid_list)) {
      print("Word not in list, try another please!")
      } else {
      guesses <- guesses + 1
# Process the guess if it's valid
      guess_vector <- strsplit(guess, "")[[1]]
# Give the player a hint
hint <- print(evaluate_guess(guess_vector, solutionvector))
# Tell player which letters are left
      letters_remaining <- setdiff(letters_remaining, guess_vector)
      print(paste("Letters remaining:", paste(letters_remaining, collapse = " ")))
      }
# Check for a correct guess
      if (all(hint == "*")) {
        print(paste("Congratulations! You've guessed the word correctly in", guesses, "guess(es)!"))}}
  print(paste("All guesses used. The solution was", solution))
  return(guesses)
}

play_wordle(solutionvector, solution_list, num_guesses = 6)
```

```{r extra_code}
# ```r
rmarkdown::render("path/to/your_document.Rmd")

```
